Large scale risks from pesticides in small streams

### 2016-10-18 cover_letter/cover.tex
typos+ grammar

\address{
    % Include the logos
    \includegraphics[width=3in]{Uni-Logo-2c.jpg}\hspace{\fill}\includegraphics[width=2in]{logo_institut.jpg}
    ~\\[-0.11in] % Reduce the whitespace above the horizontal rule
    \vhrulefill{1pt} \\ 
    \hspace{\fill}\parbox[t]{4in}{ % Create a box for your details underneath the horizontal rule on the right
        \vspace{0.2in}
        \textbf{\Who} \em \\ % Your name, all text after this will be italicized
        \Where\\ % Your department
        \Address\\ % Your address
        \CityZip\\ % Your city and zip code
        \TEL\\ % Your phone number
        \Email\\ % Your email address
    }
    \hspace{-1.4in} % Horizontal position of this block, increase to move left, decrease to move right
    \vspace{-1in} % Move the letter content up for a more compact look
}

@@

\def\opening#1{
\thispagestyle{empty}
{\centering\fromaddress \vspace{0.5in} \\} 
{\raggedright \toname \\ \toaddress \par} % Print the to name and address
\vspace{2em}
% Subject line
\noindent
\textbf{Submission of article} \hspace*{\fill}\today \\[2em]
\vspace{0.6in} % White space after the to address
\noindent #1 % Print the opening line
}

@@

\long\def\closing#1{
    \vspace{0.1in} % Some whitespace after the letter content and before the signature
    \noindent % Stop paragraph indentation
    \hspace*{\fill} % Move the signature right
    \parbox{\indentedwidth}{\raggedright
    #1 % Print the signature text
    \vskip 0.65in % Whitespace between the signature text and your name
    \fromsig}
} % Print your name and title

@@

\opening{Dear Editor,}
\vspace{-1em}\\
enclosed is a manuscript to be considered for publication in Environmental Science \& Technology titled \\

\emph{Pesticides in small streams in Germany}\\

@@

We compiled and homogenized monitoring data from all German Federal States with a focus on small to mid-size streams. 
Our results show that there is currently a lack of knowledge for small streams. 
Using new and appropriate modeling techniques we show that in the influence of agricultural land use is non-linear.
Measured pesticide concentrations are influenced by precipitation before sampling and show a temporal pattern with a peak during summer.
Especially, neonicotinoid pesticides may pose a risk to small agricultural freshwaters.

Our study should be of general interest and provides valuable information on chemical monitoring, pesticide occurrences and ecological risk arising from them.

>>>>

\address{
    % Include the logos
    \includegraphics[width=3in]{Uni-Logo-2c.jpg}\hspace{\fill}\includegraphics[width=1.5in]{logo_institut.jpg}
    ~\\[-0.11in] % Reduce the whitespace above the horizontal rule
    \vhrulefill{1pt} \\ 
    \hspace{\fill}\parbox[t]{4in}{ % Create a box for your details underneath the horizontal rule on the right
        \vspace{0.2in}
        \textbf{\Who} \em \\ % Your name, all text after this will be italicized
        \Where\\ % Your department
        \Address\\ % Your address
        \CityZip\\ % Your city and zip code
        \TEL\\ % Your phone number
        \Email\\ % Your email address
    }
    \hspace{-1.4in} % Horizontal position of this block, increase to move left, decrease to move right
    \vspace{-1in} % Move the letter content up for a more compact look
}

@@

\def\opening#1{
\thispagestyle{empty}
{\centering\fromaddress \vspace{0.5in} \\} 
{\raggedright \toname \\ \toaddress \par} % Print the to name and address
\vspace{3em}
% Subject line
\noindent
\textbf{Submission of article} \hspace*{\fill}\today \\[2em]
\vspace{0.6in} % White space after the to address
\noindent #1 % Print the opening line
}

@@

\long\def\closing#1{
    \vspace{0.4in} % Some whitespace after the letter content and before the signature
    \noindent % Stop paragraph indentation
    \hspace*{\fill} % Move the signature right
    \parbox{\indentedwidth}{\raggedright
    #1 % Print the signature text
    \vskip 0.1in % Whitespace between the signature text and your name
    \fromsig}
} % Print your name and title

@@

\opening{Dear Editor,}
\vspace{-2em}\\
enclosed is a manuscript to be considered for publication in Environmental Science \& Technology titled \\[-1em]

\emph{Large scale risks from pesticides in small streams}\\[-1em]

@@

We compiled and homogenized monitoring data from all German Federal States with a focus on small streams. 
Our results show that:
\begin{enumerate} 
\item there is currently a lack of knowledge for small streams
\item the influence of agricultural land use is non-linear with a threshold at 25\%
\item measured pesticide concentrations increase by precipitation before sampling and therefore current monitoring underestimates risks
\item show compound specific yearly dynamics that corresponds to applications
\item especially, neonicotinoids pose a risk to small agricultural freshwaters.
\end{enumerate}

Our study should be of general interest and adds valuable information on chemical monitoring, pesticide dynamics and ecological risk arising from them.
